---
title: "Data Product Final Prezi"
author: "Mohamed Elkhodary"
date: "July 16, 2017"
output:
  ioslides_presentation:
    logo: mm.jpg
---

##Full Graph App
####This is a simple full graph demonstration app,where you can change full graph size,node color and size as well as edge color and width
####Input fields will be avaiable to user in order to ernter his desired value for each variable and changes will automatically appear


##The Assignment
####**This assignment consisted of two parts:**     
1. An R Shiny application, complete with input, reactive output, and associated documentation    
2. A Reproducible Pitch Presentation in R Studio Presenter, complete with embedded R code

##R package: igraph
####igraph is used to create the network graph in this app.     
####For more detail about igraph: <http://igraph.org/>


##An example of codes for a full graph

```{r include=FALSE}
library(igraph); library(dplyr);
```

```{r fig.align='center', tidy=TRUE, tidy.opts=list(width.cutoff=55)}
plot(make_full_graph(8) %>% set_edge_attr("color", value = "blue")%>%set_edge_attr("width", value =5)%>%set_vertex_attr("color", value = "green")%>%set_vertex_attr("size", value = 10))
```
